\Large \bf Rethinking Service Systems: \\ A Path Towards Secure and Equitable Resource Markets

### 2020-06-03 CESC-submission/paper.tex
extend discussion

>>>>

Another issue is regarding the payment computation. During early stages when the network launches, we anticipate a limited adoption and service demand. Thus, we reward Ursulas for just being online to encourage adoption. While in later stages, payments will be dispensed in proportion to the actual amount of service an Ursula provides. This is due to the fact that later on the inflation rewards will disappear, i.e., all tokens in the network will be minted, and the service fees are the only source of income. To incentivize Ursula to provide a correct and timely service, these rewards should be computed based on the actual amount of service. This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
